---
title: "example-workflow"
author: "Anders Jensen"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example Worklflow for AndersR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(AndersR)
```

# Introduction

This document demonstrates how to use the functions in the **AndersR** package. This is mainly an R package to help me with proteomics analysis. If you use this package no need to cite anywhere I just hope it helps. 

## Proteomics

As I mentioned above, its mainly for proteomics analysis but there are other sections for more niche functions. 

### Read in data

Currently this package supports reading in output files from; Spectronaut, MaxQuant and ProgenesisQI. You can skip this part if you already have a clean dataset (Proteins in rows and Samples in columns)

MaxQuant - Tidy_MaxQuant
SpectroNaut - Tidy_Spectronaut
Progensis - Tidy_Progenesis

For help with these functions run ?function_name

### Produce dummy data

This function is able to generate some sample data for you to pratice with in case you are experiencing errors and also how I will show you how to use the package. 

You can specify many things about your test dataset and it is probably best to match your own. 

```{r dummy}

df <- Dummy_Data(n_proteins = 1000,
                 group1 = "control",
                 group2 = "treated",
                 n_replicates = 6,
                 missing_frac = 0.1)

head(df, 10)

```

### Tidy column names

This function and the Add_Grouping() functions are mainly here to help you tidy up your column names in cases where they are complex. 

You can do this on excel however this function will start an interactive process in the R console where you can manually input column names. Its a bit of a pain but easy enough. 

### Add grouping 

Same as above. It helps me because my column names are always messed up. 

### Make matrix


### Check filtering 

### Filter data

### Test normalisation 

### Normalise data

### Differential abundance analysis

### Convert gene names to protein 

### Summarise DA analysis

### Volcano plot

### Boxplots




